---
output: 
  pdf_document:
    latex_engine: pdflatex
    template: svm-latex-cv.tex
geometry: margin=1in
keep_tex: FALSE


title: "CV"
author: Anton Olsson-Collentine

jobtitle: "PhD candidate, Tilburg Meta-Research Center"
address: "Department of Methodology and Statistics, Tilburg University"
fontawesome: yes
email: anton@olssoncollentine.com
#github: jaeoc
# twitter: a_collentine
#osf: "ORCid: 0000-0002-4948-0178"
#phone: ""
web: olssoncollentine.com
updated: yes

keywords: R Markdown, academic CV, template

fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 11pt
linkcolor: blue
urlcolor: blue
---
 
<!-- Adapted from Steven Miller's template: http://svmiller.com/blog/2016/03/svm-r-markdown-cv/ 
For kableExtra to function I had to add some packages to the .tex preamble: \usepackage{float}, \usepackage{array}, \usepackage{booktabs}, \usepackage{tabu}-->

<!-- In addition, I have added \usepackage{titlesec} + two lines of code in .tex preamble to get lines under each header following this stackexchange question: https://tex.stackexchange.com/questions/84061/how-can-i-make-a-bold-horizontal-rule-under-each-section-title -->

<!-- Inspired also by https://github.com/marsha5813/resume  -->

\arrayrulecolor{white}
<!-- This makes all lines in the tables invisible (white), when combined with adding the package \usepackage{colortbl} to the .tex preamble. See https://stackoverflow.com/questions/53868409/is-there-a-way-to-make-a-kable-without-lines-borders-for-pdf -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(kableExtra) #for more table options when printing
```


```{r data, cache=TRUE}

#Input data for each section. New lines inside a table cell should be separated by ';'.

edu <- tibble::tribble(
  ~when, ~what,
  "2018 - present", "PhD candidate in Methodology and Statistics; Tilburg University, the Netherlands",
  "2018", "Msc. Social and Behavioral Sciences (Cum Laude);Tilburg University, the Netherlands ;Specialization: Methodology and Statistics.",
  "2016", "Bsc. Psychology ;The University of Gothenburg, Sweden"
)


appoint <- tibble::tribble(
  ~when, ~what, 
   "2019 - present", "Statistical consultant ETZ hospitals; Departmental liaison providing statistical consulting to medical researchers at the ETZ hospitals upon request by the ETZ research coordinator",
  "2020 - 2022", "PhD representative Interuniversity Graduate School of Psychometrics and Sociometrics (IOPS); Among other things, activities consisted of attending IOPS board meetings, selecting reviewers for new IOPS proposals, and chairing the IOPS PhD student meeting.",
  "2019", "Organizing committee Tilburg Meta-research Day 2019; Member of the organizing committee of an 1-day meta-research conference at Tilburg University. Plenary speakers: John Ioannidis, Ana Marušić, and Sarah de Rijcke."
)

teach <- tibble::tribble(
  ~when, ~what, 
  "2018", "Test theory (psychometrics); Tilburg University, the Netherlands",
  "2018", "Introduction to statistics; Tilburg University, the Netherlands",
  "2017", "Test theory (psychometrics); Tilburg University, the Netherlands"
  )

papers <- tibble::tribble(
  ~when, ~what,
  "2021", "Mulder, J., Williams, D. R., Gu, X., Tomarken, A., Böing-Messing, F., Olsson-Collentine, A., Meijerink-Bosman, M., Menke, J., van Aert, R., Fox, J.-P., Hoijtink, H., Rosseel, Y., Wagenmakers, E.-J., & van Lissa, C. (2021). BFpack: Flexible Bayes Factor Testing of Scientific Theories in R. Journal of Statistical Software, 100(18), 1–63. https://doi.org/10.18637/jss.v100.i18",
  "2020", "Olsson-Collentine, A., Wicherts, J. M., & van Assen, M. A. L. M. (2020). Heterogeneity in direct replications in psychology and its association with effect size. Psychological Bulletin, 146(10), 922–940. https://doi.org/10.1037/bul0000294", 
  "2020", "Maassen E, van Assen MALM, Nuijten MB, Olsson-Collentine A, Wicherts JM (2020) Reproducibility of individual effect sizes in meta-analyses in psychology. PLoS ONE 15(5): e0233107. https://doi.org/10.1371/journal.pone.0233107",
  "2019", "Olsson-Collentine, A., van Assen, M. A. L. M., & Hartgerink, C. H. J. (2019). The Prevalence of Marginally Significant Results in Psychology Over Time. Psychological Science, 30(4), 576–586. https://doi.org/10.1177/0956797619830326",
  "2019", "Mulder, J. & Olsson-Collentine, A. (2019). Simple Bayesian testing of scientific expectations in linear regression models. Behavior Research Methods. https://doi.org/10.3758/s13428-018-01196-9",
  "Accepted", "van Aert, R. C. M., Nuijten, M. B., Olsson-Collentine, A., Stoevenbelt, A. H.,vandenAkker,O.,& Wicherts,J.M.(2021). Comparing the prevalence of statistical reporting inconsistencies in COVID-19 preprints and matched controls: A Registered Report (Stage 1). Royal Society Open Science. Conditionally accepted",
  "Submitted", "Olsson-Collentine, A., van Aert, R. C. M., Bakker, M., & Wicherts, J. M. (2021). Meta-analyzing the multiverse: A peek under the hood of selective reporting. doi:10.31234/osf.io/43yae",
  "Submitted", "van Assen, M. A. L. M., van den Akker, O. R., Augusteijn, H. E. M., Bakker,M.,Nuijten,M.B.,Olsson-Collentine,A.,Stoevenbelt,A.H.,Wicherts,J.M.,& van Aert, R. C. M. (2021). The meta-plot: A graphical tool for interpreting the results of a meta-analysis."
)

talk <- tibble::tribble(
  ~when,  ~what,
  "2021", 'Metascience 2021 conference; "Meta-analyzing the multiverse: A peek under the hood of selective reporting"',
  "2021", 'AIP LECCE 2021 conference; "Confidence in hypothesis-testing with a multiverse of outcomes"', 
  "2020", 'IOPS winter conference 2020; "Meta-analyzing the multiverse: A peek under the hood of selective reporting"',
  "2019", 'Platform for Young Meta-Scientists (PYMS); Tilburg, the Netherlands; "Vague theory, unmotivated choices, and exaggerated conclusions"',
  "2019", 'Open Science 2019 conference; Trier, Germany; "Heterogeneity in direct replications in psychology and its association with effect size"',
  "2019", 'ICPS Paris conference; Paris, France; "Heterogeneity in direct replications in psychology and its association with effect size"',
  "2018", 'EPP Meta-Analysis Symposium (invited talk); Heeze, the Netherlands; "Heterogeneity and Publication bias"'
)

memberships <- c(
  "Society for Improvement of Psychology (SIPS)",
  "Interuniversity Graduate School of Psychometrics and Sociometrics (IOPS)",
  "Psychological Science Accelerator (PSA)",
  "Society for Open, Reliable, and Transparent Ecology and Evolutionary biology (SORTEE)"
)

grants_awards <- tibble::tribble( #not currently implemented
  ~when, ~what,
  "2019", "Research Synthesis PhD Travel Grant (200€); Travel grant to participate in the Research Synthesis 2019 conference" 
)

supervision <- tibble::tribble( #not currently implemented
  ~when, ~what,
  "Oct 2020 - Feb 2021", "Supervisor Sep Hesselmans; Bachelor thesis: Construct validity in Registered Replication Reports"
)
```


```{r table_functions}
#Function to format the input data and make it ready for printing

format_output <- function(input){
  #Make text until first ';' bold
  text_to_bold <- unlist(lapply(strsplit(input$what, split = ";"), function(x) x[[1]])) #extract until first ';' for each data point
  text_to_bold <- gsub("\\(", "\\\\(", text_to_bold) #any left parentheses must be escaped so gsub works in next step 
  input$what <- mapply(gsub, text_to_bold, paste0("\\\\textbf{", text_to_bold, "}"), input$what) #replace by (latex) bold version, mapply loops over each data point
  
  #make a linebreak after each ';' when printing table (linebreak function adds some latex code)
  input$what <- kableExtra::linebreak(input$what, linebreaker = ";")
  
  input
}


#function to create tables
CV_table <- function(x){
  knitr::kable(x, booktabs = TRUE, col.names = NULL, escape= FALSE, linesep = "\\addlinespace") %>% 
  column_spec(1,"2.5cm", bold = TRUE) %>% 
  column_spec(2, "13.3cm")}
```

```{r format-data}
input <- list(education = edu,
              appointments = appoint,
              teaching = teach,
              supervision = supervision,
              grants = grants_awards,
              talks = talk)

input <- lapply(input, format_output)

#For education and academic appointments [edit: removed], add empty row after each row so that there is space between entries in the output
input[c("education")] <- lapply(input[c("education")], function(x) sapply(x, rbind, ""))

#add papers to list, which needs different formatting
input$papers <- papers
input$papers$what <- gsub("Olsson-Collentine", "\\\\textbf{Olsson-Collentine}", input$papers$what) #bold
input$papers$what <- gsub("&", "\\\\&", input$papers$what) #& must be escaped
```


\vspace{1.2cm}
<!-- Adds some vertical spacing between header and rest -->

# Education

`r input$education %>% CV_table()`

# Academic appointments

`r input$appointments %>% CV_table()`

# Publications

`r input$papers %>% CV_table()`

# Presentations

`r input$talks %>% CV_table()`

# Grants

`r input$grants %>% CV_table()`

# Teaching (tutorials)

`r input$teaching %>% CV_table()`

# Supervision

`r input$supervision %>% CV_table()`

# Professional memberships

`r knitr::kable(memberships, booktabs = TRUE, col.names = NULL, escape= FALSE, linesep = "\\addlinespace")` 

